HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-08 scnn.tex
update link convolution

    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
    \item (done!) (NP) make figure A.13 remove white space
    \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
    \item (NP) vertex interpretation
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
\end{equation}
We would like to emphasis that traditional convolution can be written in the same form as \eqnref{graph_convolution_spatial}. Given $f,g$ two 1 dimentional discrete signals, their convolution can be written as
\begin{equation}
(f \ast g) (n) = \sum_{m=-\infty}^\infty f(m) g(n-m) = \langle T_n g,  f \rangle,
\end{equation}
where $T_n g(m)=g(n-m)$ is (up to a flip) a translation operator.

>>>>

    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
    \item (done!) (NP) make figure A.13 remove white space
    \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph. It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
This localization of the kernel $h$ can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another. While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular. However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with the localizations of the kernel $h$, i.e. 
\begin{equation} \label{eqn:graph_convolution_spatial}
	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
\end{equation}
We would like to emphasis that traditional convolution can be written in the same form as \eqnref{graph_convolution_spatial}. Given $f,g$ two 1 dimentional discrete signals, their convolution can be written as
\begin{equation} \label{eqn:standard_convolution}
(f \ast g) (n) = \sum_{m=-\infty}^\infty f(m) g(n-m) = \langle T_n g,  f \rangle,
\end{equation}
where $T_n g(m)=g(n-m)$ is, up to a flip, a translation operator. As a result, the convolution is simply the scalar product with the translated kernel $g$.
Additionally to the fact that \eqnref{graph_convolution_spatial} and \eqnref{standard_convolution} are both scalar product, it turns out that the localization operator $h(\L) \b \delta_i$ is some generalization of the translation for graphs. Furthermore that in the particular case where the Laplacian matrix $\L$ is circulant, $h(\L) \b \delta_i$ is a translated version of $h(\L) \b \delta_j$ for all $i,j$ and both convolution are equivalent.
For a detailled explanation of the connection between translation and localization, refer to \citep[Sec 2.2]{perraudin2017stationary}.
